---
title: "Prediction Assignment"
output: html_document
---
## Practical Machine Learning: Prediction Assignment

We load the training and test data.
```{r}
training<-read.csv("pml-training.csv")
testing<-read.csv("pml-testing.csv")

```

We do some exploratory analyses first and then we clean the data to eliminate NA columns.

```{r, warning=FALSE,results='hide',fig.keep='none'}
str(training)
plot(training$classe)
colSums(is.na(training))
training<-training[, colSums(is.na(training))+colSums(is.na(testing)) == 0]
testing<-testing[, colSums(is.na(training))+colSums(is.na(testing)) == 0]
```

We will fit a Random Forest model, in order to predict the "classe" factor variable.

Since the "classe" variable is not continous, we will use the Accuracy as error measure.

Additionally, we will use parallel processing to make the model usable.

```{r, cache=TRUE}
library(parallel)
library(doParallel)
cluster <- makeCluster(detectCores() - 1) 
registerDoParallel(cluster)

library(caret)
set.seed(20)
modFit_ctrl<-trainControl(method="cv",number=5,allowParallel=TRUE)

modFit <- train(classe ~ ., data = training,
                    method = "rf",
                    preProcess = c("center","scale"),

                    trControl = modFit_ctrl)

stopCluster(cluster)
modFit
confusionMatrix.train(modFit)
pred1<-predict(modFit,testing)
(1-0.9998)*100
```

Finally, we check that the Accuracy is above 99% and predict 20 test cases.

The out of sample error is estimated at 0.02%.

```{r}

```
